### 2020-01-27 latex/sections/background.tex
latex work

>>>>

\subsection{Explainable Artificial Intelligence}

Within XAI many methods have been developed to try to evaluate
ANN's, these methods are often referred as model interpretability methods.
In the field image recognition there has been a lot of work examining which
pixels of an image the model deems important. Arguably the most popular
method for this is Saliency Maps (CITE ME). There the pixel values the model
deems important are colored in s.t. a human can examine the image and get a
sense of what portions of the image are important to the model, an example of
a classification of a dog can be seen in Figure \ref{fig:dog_saliency}.

\begin{figure}[]
  \centering
  \includegraphics[width=.5\textwidth]{graphics/dog_saliency}
  \caption{Example of a models saliency map for an image of a dog}
  \label{fig:dog_saliency}
\end{figure}

### 2020-01-27 latex/sections/introduction.tex
latex work

In the world of deep learning is exciting, we have models that are able to examine
images and very reliably be able to identify it's content. Deep learning models have
beaten Opthalmologists in identifing diabetic retinopathy, they've identified
cancer cells where others have not. Deep learning models have even predicted
the likelyhood a person will die in the following year. These models have done
these things extremely accurately, cheap, and fast. These successes allow us to
dream of a future where all things are eventually possible with the help of
technology.

The field of examining deep learning models to gain a richer understanding
in how they work, and what makes them so much better than humans at various tasks
is still new. This is the field of Explainable Artificial Intelligence (XAI).
If we wish to continue using artificial intelligence (AI) and machine learning (ML),
to improve our lives we must examine how they work, this is not only to improve
ourselves but these explanations are a legal requirement now in many areas, namely, legal, and
medical.

@@

>>>>

In the world of deep learning is exciting, we have models that are able to examine
images and very reliably be able to identify it's content. Deep learning models have
beaten Opthalmologists in identifing diabetic retinopathy, they've identified
cancer cells where others have not. Deep learning models have even predicted
the likelyhood a person will die in the following year with good accuracy (CITE).
These models have done these things extremely accurately, cheap, and fast.

The field of examining deep learning models to gain a richer understanding
in how they work, and what makes them so much better than humans at various tasks
is still new. This is the field of Explainable Artificial Intelligence (XAI).
If we wish to continue using artificial intelligence (AI) and machine learning (ML),
to improve our lives we must examine how they work, this is not only to improve
ourselves but these explanations are a legal requirement now in many areas, namely, legal, and
medical. Recently, XAI has generally been focused on Model Interpretability, in
particular focus on gaining insights on the concepts learned by Deep Neural Networks.

@@

The method of examining HLC's within games has generally been done by examining the
current state of the game by evaluating them w.r.t. a heuristic. A heuristic within
games are a evaluation of the end cost for a state given just the state, for example,
the amount of pieces left within a game of chess. Intuitively, the amount of pieces
left is a good estimate for a state in chess, this is a higher level concept we
use to evaluate a chess position. The piece amount is much lower level than other
concepts we use, grand master chess players evaluate a position w.r.t. states
where the king is safe from attack, or the structure of the pawn positions.
The idea is to examine a neural networks evaluation of a state regarding
those higher level concepts, if human players evaluate the king safety of a state
low but the neural network highly values it, and the neural network plays better
than the player. There is reason for us to consider a new way to play.
